Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-08-01 Moltres.tex
nouns to verbs

Moltres is an open source code licensed under \gls{LGPL} terms that aims to be a
tool that can be freely used, studied, interrogated, and improved by the
\gls{MSR} community.  Its openness is a defining characteristic and promotes
quality through transparency and ease of peer review. In the era of
GitHub\cite{noauthor_build_nodate} and international scientific collaboration,
open and modern software practices must be employed in order for nuclear
engineering simulation capability to enable discovery and support the regulatory
needs presented by new reactor designs. In that vein, Moltres uses
\mintinline{latex}{git} for version control, integration testing to protect
developed physics capabilities, and a C++ object-oriented design to
enable extension and code reuse. Moreover, Moltres is built on
top of the \gls{MOOSE} framework, \cite{gaston_physics-based_2015} another
\gls{LGPL} code that itself leans on LibMesh \cite{kirk_libmesh:_2006}, a
\gls{LGPL} finite element library, and PetSc \cite{satish_balay_petsc_2015}, a
\gls{BSD}-licensed toolkit for solving nonlinear equations stemming from
discretization of PDEs. \gls{MOOSE} and LibMesh handle translation of
application (Moltres) defined weak PDE forms into residual and Jacobian
functions that are the inputs into PetSc Newton-Raphson solution routines. All
codes use MPI for parallel communication and are easily deployed on
massively-parallel cluster-computing platforms. \gls{MOOSE} applications by
default use monolithic and implicit methods that are ideal for closely-coupled
and multi-scale physics. These methods are ideal for the model problem described
in this work. However, it should be noted that Moltres can also use explicit
time-stepping routines as well as segregated solution methods, making it very
extensible to myriad future modeling challenges.

>>>>

Moltres is an open source code licensed under \gls{LGPL} terms that aims to be a
tool that can be freely used, studied, interrogated, and improved by the
\gls{MSR} community.  Its openness is a defining characteristic and promotes
quality through transparency and ease of peer review. In the era of
GitHub\cite{noauthor_build_nodate} and international scientific collaboration,
open and modern software practices must be employed in order for nuclear
engineering simulation capability to enable discovery and support the regulatory
needs presented by new reactor designs. In that vein, Moltres uses
\mintinline{latex}{git} for version control, integration testing to protect
developed physics capabilities, and a C++ object-oriented design to
enable extension and code reuse. Moreover, Moltres is built on
top of the \gls{MOOSE} framework, \cite{gaston_physics-based_2015} another
\gls{LGPL} code that itself leans on LibMesh \cite{kirk_libmesh:_2006}, a
\gls{LGPL} finite element library, and PetSc \cite{satish_balay_petsc_2015}, a
\gls{BSD}-licensed toolkit for solving nonlinear equations yielded by 
discretizing PDEs. \gls{MOOSE} and LibMesh translate weak PDE forms defined by
applications (e.g. Moltres) into residual and Jacobian
functions that are the inputs into PetSc Newton-Raphson solution routines. All
codes use MPI for parallel communication and are easily deployed on
massively-parallel cluster-computing platforms. \gls{MOOSE} applications by
default use monolithic and implicit methods that are ideal for closely-coupled
and multi-scale physics. These methods are ideal for the model problem described
in this work. However, it should be noted that Moltres can also use explicit
time-stepping routines as well as segregated solution methods, making it very
extensible to myriad future modeling challenges.
